Alex's Notes and Text Fragments for the JSS Manuscript

### 2024-01-30 paper/article.Rmd
fix missing refs

Compared to other existing machine-learning frameworks in R (e.g., \pkg{caret} [@kuhn2020] or \pkg{tidymodels} [@tidymodels]), \pkg{mlr3} is the only one that provides a dedicated object-oriented framework for spatial and spatiotemporal resampling methods.
In addition \pkg{mlr3} uses efficient core dependencies from the \pkg{data.table} [@datatable] and \pkg{R6} [@r6] packages, which are particularly well suited for large datasets.
Through this object-oriented approach, \pkg{mlr3} uses substantially less memory than other frameworks due to the use of pointer references and the avoidance of deep object copies whenever possible [@mlr3book].

>>>>

Compared to other existing machine-learning frameworks in R (e.g., \pkg{caret} [@kuhn2020] or \pkg{tidymodels} [@kuhn2020]), \pkg{mlr3} is the only one that provides a dedicated object-oriented framework for spatial and spatiotemporal resampling methods.
In addition \pkg{mlr3} uses efficient core dependencies from the \pkg{data.table} [@datatable] and \pkg{R6} [@r6] packages, which are particularly well suited for large datasets.
Through this object-oriented approach, \pkg{mlr3} uses substantially less memory than other frameworks due to the use of pointer references and the avoidance of deep object copies whenever possible [@mlr3book].
